---
title: "Erick David Rodriguez-Orduna, B.E.E."
output:
    html_document:
        df_print: paged
runtime:shiny

---

Hello and welcome to my website.

I'm Erick David Rodriguez-Orduna, Bachelor of Electronical Engineering from Universidad de las Americas Puebla [UDLAP](https://www.udlap.mx/web){target="_blank"}

Currently I'm pursuing the Ph.D in Intelligent Systems from same institution.

In this website I will include some my work as a PhD student, which can be related or not related to the Doctoral Thesis topic.

Since my Doctoral program is a Full-Time study I don't have enough time to develop another projects but I also have strong interest in Data-Science and Economical-Finance areas, therefore I will also upload some of that work too.

I have experience coding in some programming languages:


*Experienced:*

- Python
- R

*Not that experienced:*

- C++
- SQL
- MATLAB
- Mosel from XPRESS
- Verilog









The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.


```{r}
x= c(1,2,3,4)
y= c(2,2,2,5)
plot(x,y)
lines(x,y)
```
```{r}
plot(y,x)
lines(y,x)
```

```{r}

```
```{r echo = FALSE}
# Define UI for app that draws a histogram ----
ui <- fluidPage(

    # App title ----
    titlePanel("Hello Shiny!"),

    # Sidebar layout with input and output definitions ----
    sidebarLayout(

        # Sidebar panel for inputs ----
        sidebarPanel(

            # Input: Slider for the number of bins ----
            sliderInput(inputId = "bins",
                label = "Number of bins:",
                min = 1,
                max = 50,
                value = 30)

        ),

        # Main panel for displaying outputs ----
        mainPanel(

            # Output: Histogram ----
            plotOutput(outputId = "distPlot")

        )
    )
)
# Define server logic required to draw a histogram ----
server <- function(input, output) {

# Histogram of the Old Faithful Geyser Data ----
# with requested number of bins
# This expression that generates a histogram is wrapped in a call
# to renderPlot to indicate that:
#
# 1. It is "reactive" and therefore should be automatically
#    re-executed when inputs (input$bins) change
# 2. Its output type is a plot
    output$distPlot <- renderPlot({

        x    <- faithful$waiting
        bins <- seq(min(x), max(x), length.out = input$bins + 1)

        hist(x, breaks = bins, col = "#75AADB", border = "white",
        xlab = "Waiting time to next eruption (in mins)",
        main = "Histogram of waiting times")

    })

}
shinyApp(ui, server)
```
