---
title: "Erick David Rodriguez-Orduna, B.E.E."
output:
html_document:
df_print: paged
---

Hello and welcome to my website.

I'm Erick David Rodriguez-Orduna, Bachelor of Electronical Engineering from Universidad de las Americas Puebla [UDLAP](https://www.udlap.mx/web){target="_blank"}

Currently I'm pursuing the Ph.D in Intelligent Systems from same institution.

In this website I will include some my work as a PhD student, which can be related or not related to the Doctoral Thesis topic.

Since my Doctoral program is a Full-Time study I don't have enough time to develop another projects but I also have strong interest in Data-Science and Economical-Finance areas, therefore I will also upload some of that work too.

I have experience coding in some programming languages:

1. Experienced
    -Python
    -R

2. Not that experienced
-C++
-SQL









The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.


```{r}
x= c(1,2,3,4)
y= c(2,2,2,5)
plot(x,y)
lines(x,y)
```
```{r}
plot(y,x)
lines(y,x)
```

```{r}
```